---
title: "Curriculum Vitae"
author:
  firstname: Gidon T.
  lastname: Frischkorn
  address: "Binzmühlerstrasse 14/22 - CH-8050 Zurich, Switzerland"
  position: "Cognitive Psychometrics · Bayesian Methods · Intelligence Research"
  contacts:
    - icon: fa envelope
      text: gidon.frischkorn@unilu.ch
      url: "mailto:gidon.frischkorn@unilu.ch"
    - icon: fa link
      text: gfrischkorn.org
      url: "https://www.gfrischkorn.org"
    - icon: fa brands github
      text: GidonFrischkorn
      url: "https://github.com/GidonFrischkorn"
    - icon: fa brands orcid
      text: 0000-0002-7340-3409
      url: "https://orcid.org/0000-0002-7340-3409"
format:
  awesomecv-typst:
    keep-typ: false
knitr:
  opts_chunk:
    dev: png
    fig.show: hide
execute:
  echo: false
  output: asis
---

```{r}
#| label: setup
#| include: false
source("helpers.R")
lang <- "en"
```

# Education

```{r}
render_education(lang)
```

# Professional Experience

```{r}
render_work(lang)
```

# Shortlisted in Appointment Procedures

```{r}
render_appointments(lang)
```

# Language Skills

```{r}
render_languages(lang)
```

# Awards, Honors, and Fellowships

```{r}
render_awards(lang)
```

```{=typst}
#pagebreak()
```

# Third-Party Funding

```{r}
render_funding(lang, include_summaries = TRUE)
```

## Travel Awards

```{r}
render_travel_awards(lang)
```

# Publications and Research Contributions

```{r}
render_citation_stats(lang)
```

## Software

```{r}
render_software(lang)
```

## Preprints

```{r}
render_publications("preprints", lang)
```

## Peer-Reviewed Journal Articles

```{r}
render_publications("articles", lang)
```

# Presentations

## Talk Series

```{r}
data <- yaml::read_yaml("data/presentations.yml")
ts <- data$talk_series[[1]]
typst_block(typst_entry(
  title = get_lang(ts$title, lang),
  date = as.character(ts$year),
  description = get_lang(ts$description, lang)
))
```

## Invited Talks

```{r}
render_invited_talks(lang)
```

## Conference Contributions

```{r}
render_conference_summary(lang)
```

```{=typst}
#pagebreak()
```

# Teaching

```{r}
data <- yaml::read_yaml("data/teaching.yml")
typst_block(sprintf("Overview of teaching (since 2015, summarized): %s\n", get_lang(data$overview, lang)))
```

## Lectures

```{r}
render_lectures(lang)
```

## Seminars

```{r}
render_seminars(lang)
```

## Workshops

```{r}
render_workshops(lang)
```

## Higher Education Professional Development

```{r}
data <- yaml::read_yaml("data/teaching.yml")
entries <- vapply(data$professional_development, function(entry) {
  typst_entry(
    title = get_lang(entry$title, lang),
    date = entry$date,
    description = get_lang(entry$details, lang)
  )
}, character(1))
typst_block(entries)
```

## Thematic Breadth

```{r}
data <- yaml::read_yaml("data/teaching.yml")
breadth <- get_lang(data$breadth, lang)
bullets <- paste0("- ", breadth, collapse = "\n")
typst_block(bullets)
```

# Engagement in the Scientific Community

## Editorial Roles

```{r}
render_editorial(lang)
```

## Reviewing

```{r}
render_reviewing(lang)
```

## Memberships

```{r}
render_memberships(lang)
```

# Engagement in Academic Self-Governance

```{r}
render_self_governance(lang)
```
